Maximum Allowable Current Determination of Arbitrary Reconfigurable Battery Systems By Using a Directed Graph Model Combined with Greedy Algorithm

### 2023-07-09 paper/SST_main.tex
解决了 SST 期刊的参考文献问题

%%%%%% Bibliography %%%%%%
% Replace "sample" in the \addbibresource line below with the name of your .bib file.
\usepackage[style=nejm, 
citestyle=numeric-comp,
sorting=none]{biblatex}
\addbibresource{main.bib}

@@

\printbibliography

>>>>

%%%%%% Bibliography %%%%%%
% Replace "sample" in the \addbibresource line below with the name of your .bib file.
% \usepackage[style=nejm, 
% citestyle=numeric-comp,
% sorting=none]{biblatex}
% \addbibresource{main.bib}

@@

\begin{thebibliography}{99}

\bibitem{desiqueiraControlStrategySmooth2021}
Luanna Maria~Silva {de Siqueira} and Wei Peng.
\newblock Control strategy to smooth wind power output using battery energy
  storage system: {{A}} review.
\newblock {\em Journal of Energy Storage}, 35:102252, March 2021.

\bibitem{yangBatteryEnergyStorage2018}
Yuqing Yang, Stephen Bremner, Chris Menictas, and Merlinde Kay.
\newblock Battery energy storage system size determination in renewable energy
  systems: {{A}} review.
\newblock {\em Renewable and Sustainable Energy Reviews}, 91:109--125, August
  2018.

\bibitem{choCommercialResearchBattery2015}
Jaephil Cho, Sookyung Jeong, and Youngsik Kim.
\newblock Commercial and research battery technologies for electrical energy
  storage applications.
\newblock {\em Progress in Energy and Combustion Science}, 48:84--101, June
  2015.

\bibitem{zhangDevelopmentProspectChinese2021}
Lihua Zhang.
\newblock Development and {{Prospect}} of {{Chinese Lunar Relay Communication
  Satellite}}.
\newblock {\em Space: Science \& Technology}, 2021, January 2021.

\bibitem{schwanbeckInternationalSpaceStation2019}
Eugene Schwanbeck and Penni Dalton.
\newblock International {{Space Station Lithium-ion Batteries}} for {{Primary
  Electric Power System}}.
\newblock In {\em 2019 {{European Space Power Conference}} ({{ESPC}})}, pages
  1--1. {IEEE}, September 2019.

\bibitem{yangUnbalancedDischargingAging2016}
Naixing Yang, Xiongwen Zhang, BinBin Shang, and Guojun Li.
\newblock Unbalanced discharging and aging due to temperature differences among
  the cells in a lithium-ion battery pack with parallel combination.
\newblock {\em Journal of Power Sources}, 306:733--741, February 2016.

\bibitem{fengPropagationMechanismsDiagnosis2019}
Fei Feng, Xiaosong Hu, Lin Hu, Fengling Hu, Yang Li, and Lei Zhang.
\newblock Propagation mechanisms and diagnosis of parameter inconsistency
  within {{Li-Ion}} battery packs.
\newblock {\em Renewable and Sustainable Energy Reviews}, 112:102--113,
  September 2019.

\bibitem{jeevarajanBatterySafetyQualifications2012}
J.~A. Jeevarajan and C.~Winchester.
\newblock Battery {{Safety Qualifications}} for {{Human Ratings}}.
\newblock {\em Interface magazine}, 21(2):51--55, January 2012.

\bibitem{pomboHybridPowerSystem2021}
Daniel~V{\'a}zquez Pombo.
\newblock A {{Hybrid Power System}} for a {{Permanent Colony}} on {{Mars}}.
\newblock {\em Space: Science \& Technology}, 2021, January 2021.

\bibitem{hanNextGenerationBatteryManagement2020a}
Weiji Han, Torsten Wik, Anton Kersten, Guangzhong Dong, and Changfu Zou.
\newblock Next-{{Generation Battery Management Systems}}: {{Dynamic
  Reconfiguration}}.
\newblock {\em IEEE Industrial Electronics Magazine}, 14(4):20--31, December
  2020.

\bibitem{visairoReconfigurableBatteryPack2008}
H.~Visairo and P.~Kumar.
\newblock A reconfigurable battery pack for improving power conversion
  efficiency in portable devices.
\newblock In {\em 2008 7th {{International Caribbean Conference}} on
  {{Devices}}, {{Circuits}} and {{Systems}}}, pages 1--6. {IEEE}, April 2008.

\bibitem{heExploringAdaptiveReconfiguration2013}
Liang He, Lipeng Gu, Linghe Kong, Yu~Gu, Cong Liu, and Tian He.
\newblock Exploring {{Adaptive Reconfiguration}} to {{Optimize Energy
  Efficiency}} in {{Large-Scale Battery Systems}}.
\newblock In {\em 2013 {{IEEE}} 34th {{Real-Time Systems Symposium}}}, pages
  118--127, December 2013.

\bibitem{hongwenheStateofChargeEstimationLithiumIon2011}
Hongwen He, Rui Xiong, Xiaowei Zhang, Fengchun Sun, and JinXin Fan.
\newblock State-of-{{Charge Estimation}} of the {{Lithium-Ion Battery Using}}
  an {{Adaptive Extended Kalman Filter Based}} on an {{Improved Thevenin
  Model}}.
\newblock {\em IEEE Transactions on Vehicular Technology}, 60(4):1461--1469,
  May 2011.

\bibitem{mousavig.VariousBatteryModels2014}
S.M. Mousavi~G. and M.~Nikdel.
\newblock Various battery models for various simulation studies and
  applications.
\newblock {\em Renewable and Sustainable Energy Reviews}, 32:477--485, April
  2014.

\bibitem{lawsonSoftwareConfigurableBattery2012}
Barrie Lawson.
\newblock A {{Software Configurable Battery}}.
\newblock {\em EVS26 International Battery, Hybrid and Fuel Cell Electric
  Vehicle Symposium}, 2012.

\bibitem{ciNovelDesignAdaptive2007}
Song Ci, Jiucai Zhang, Hamid Sharif, and Mahmoud Alahmad.
\newblock A {{Novel Design}} of {{Adaptive Reconfigurable Multicell Battery}}
  for {{Power-Aware Embedded Networked Sensing Systems}}.
\newblock In {\em {{IEEE GLOBECOM}} 2007-2007 {{IEEE Global Telecommunications
  Conference}}}, pages 1043--1047, November 2007.

\bibitem{alahmadBatterySwitchArray2008}
Mahmoud Alahmad, Herb Hess, Mohammad Mojarradi, William West, and Jay Whitacre.
\newblock Battery switch array system with application for {{JPL}}'s
  rechargeable micro-scale batteries.
\newblock {\em Journal of Power Sources}, 177(2):566--578, March 2008.

\bibitem{kimDependableEfficientScalable2010b}
Hahnsang Kim and Kang~G. Shin.
\newblock Dependable, efficient, scalable architecture for management of
  large-scale batteries.
\newblock In {\em Proceedings of the 1st {{ACM}}/{{IEEE International
  Conference}} on {{Cyber-Physical Systems}}}, {{ICCPS}} '10, pages 178--187,
  {New York, NY, USA}, April 2010. {Association for Computing Machinery}.

\bibitem{kimBalancedReconfigurationStorage2011a}
Younghyun Kim, Sangyoung Park, Yanzhi Wang, Qing Xie, Naehyuck Chang, Massimo
  Poncino, and Massoud Pedram.
\newblock Balanced reconfiguration of storage banks in a hybrid electrical
  energy storage system.
\newblock In {\em 2011 {{IEEE}}/{{ACM International Conference}} on
  {{Computer-Aided Design}} ({{ICCAD}})}, pages 624--631, November 2011.

\bibitem{taesickimSeriesconnectedSelfreconfigurableMulticell2012a}
Taesic Kim, Wei Qiao, and Liyan Qu.
\newblock A series-connected self-reconfigurable multicell battery capable of
  safe and effective charging/discharging and balancing operations.
\newblock In {\em 2012 {{Twenty-Seventh Annual IEEE Applied Power Electronics
  Conference}} and {{Exposition}} ({{APEC}})}, pages 2259--2264, February 2012.

\bibitem{6843711}
Liang He, Linghe Kong, Siyu Lin, Shaodong Ying, Yu~Gu, Tian He, and Cong Liu.
\newblock Reconfiguration-assisted charging in large-scale {{Lithium-ion}}
  battery systems.
\newblock In {\em 2014 {{ACM}}/{{IEEE International Conference}} on
  {{Cyber-Physical Systems}} ({{ICCPS}})}, pages 60--71, April 2014.

\end{thebibliography}

### 2023-07-09 paper/main.tex
解决了 SST 期刊的参考文献问题

\begin{abstract}
    Reconfigurable Battery Systems (RBSs) present a promising alternative to traditional battery systems due to their flexible and dynamically changeable topological structure subjected to battery charging and discharging strategies.
    During the operation of the RBS, the Maximum Allowable Current (MAC) is a critical indicator to guide the system's reconfiguring control, ensuring safety and reliability.
    In this paper, we propose a calculation method for the MAC of arbitrary RBS using a greedy algorithm in conjunction with a directed graph model of the RBS.
    By employing the directed graph model, the greedy algorithm guides the RBS to establish parallel connections among batteries, aiming to maximize the system's output current while ensuring that none of the batteries are overloaded or short-circuited.
    The effectiveness of this method is validated on a novel and complex RBS structure.
    The results demonstrate the effectiveness of this method and its potential in facilitating next-generation RBS designs and applications, including battery isolation.

>>>>

\begin{abstract}
    Reconfigurable Battery Systems (RBSs) present a promising alternative to traditional battery systems due to their flexible and dynamically changeable topological structure subjected to battery charging and discharging strategies
    During the operation of the RBS, the Maximum Allowable Current (MAC) is a critical indicator to guide the system's reconfiguring control, ensuring safety and reliability.
    In this paper, we propose a calculation method for the MAC of arbitrary RBS using a greedy algorithm in conjunction with a directed graph model of the RBS.
    By employing the directed graph model, the greedy algorithm guides the RBS to establish parallel connections among batteries, aiming to maximize the system's output current while ensuring that none of the batteries are overloaded or short-circuited.
    The effectiveness of this method is validated on a novel and complex RBS structure.
    The results demonstrate the effectiveness of this method and its potential in facilitating next-generation RBS designs and applications, including battery isolation.
